They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-13 presentation.qmd
re-render pres

```{r}
#| label: descriptive-cod-snd-stats
#| eval: true
cod_n_series <- cod_rounds |> 
  distinct(year, sheet, series) |> 
  nrow() |> 
  scales::comma()

cod_n_rounds <- cod_rounds |> 
  distinct(year, sheet, series, round) |> 
  nrow() |> 
  scales::comma()

@@

@@

@@

@@

  actual_round_streaks <- rounds |> 
    filter(round <= (.max_round - .adj)) |> 
    filter(win_series) |> 
    mutate(across(win_round, as.integer)) |> 
    group_by(series_id) |> 
    summarize(
      wins = max(cumu_w),
      losses = max(cumu_l),
      ws = paste0(win_round, collapse = '')
    ) |> 
    ungroup() |> 
    mutate(n_rounds = wins + losses) |> 
    unite(
      record, wins, losses, sep = '-'
    ) |>
    count(record, n_rounds, ws, sort = TRUE) |> 
    mutate(prop = n / sum(n))

@@

```{r}
load_qs('cod_round_win_prop_after_x_wins_y_rounds')
ggsci_orange <- extract_ggsci_mid_color('orange')
p_cod_round_win_prop_after_x_wins_y_rounds <- cod_round_win_prop_after_x_wins_y_rounds |> 
  mutate(
    is_signif = case_when(
      gt_is_signif ~ 'Better',
      lt_is_signif ~ 'Worse',
      TRUE ~ 'Neither'
    )
  ) |> 
  # filter(win_streak %in% c(3, 4)) |> 
  # filter(n >= 20) |> 
  ggplot() +
  geom_tile(
    color = blackish_background,
    height = 0.8,
    aes(
      fill = is_signif,
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  geom_richtext(
    fill = NA_character_,
    label.color = NA_character_,
    family = font,
    color = blackish_background,
    size = 11 / .pt,
    fontface = 'bold',
    aes(
      label = sprintf(
        '%s %s <span style="color:white">%s</span><br/>(%s)',
        scales::percent(prop, accuracy = 1), 
        case_when(
          round(prop, 1) == round(expected_poststreak_p, 1) ~ '=',
          prop >= expected_poststreak_p ~ '>=', 
          TRUE ~ '<'
        ),
        scales::percent(expected_poststreak_p, accuracy = 1),
        scales::comma(n)
      ),
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  guides(
    fill = guide_legend(
      'Significantly better/worse?'
    )
  ) +
  scale_x_continuous(
    labels = 4:11,
    breaks = seq(4.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  scale_fill_manual(
    values = c(ggsci_cyan, ggsci_grey, ggsci_orange),
    labels = c('Better', 'Neither', 'Worse')
  ) +
  theme(
    legend.position = 'top',
    legend.text = element_text(color = 'white', size = 12),
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Post win streak round win %',
    x = 'Round',
    y = '# of rounds played in series'
  ) +
  facet_wrap(~win_streak)
p_cod_round_win_prop_after_x_wins_y_rounds
```

@@

plot_round_vs_post_round_slope_chart <- function(df, .roun) {
  game <- match.arg(game)
  o_win_rx_prop <- summarize_map_o_round_win_prop(df, .round)
  x1_label <- sprintf('Round %d<br/>offensive win %%', .round)
  x2_label <- sprintf('Post-round %d<br/>offensive win %%', .round)

>>>>

```{r}
#| label: descriptive-cod-snd-stats
#| eval: true
cod_n_series <- cod_rounds |> 
  distinct(series_id, team) |> 
  nrow() |> 
  scales::comma()

cod_n_rounds <- cod_rounds |> 
  distinct(series_id, team, round) |> 
  nrow() |> 
  scales::comma()

@@

cod_rounds |> 
  filter(is_offense) |> 
  count(game, win_round) |> 
  group_by(game) |> 
  mutate(prop = n / sum(n)) |> 
  ungroup() |> 
  filter(win_round)

@@

all_possible_outcomes <- tibble(
  n_rounds = 6L:11L
) |> 
  mutate(
    x = map_dbl(n_rounds, ~sample(c(0L, 1L), size = .x, replace = TRUE))
  )

@@

summarize_round_arrangements <- function(rounds, .max_round, .adj = 0) {
  rounds |> 
    filter(round <= (.max_round - .adj)) |> 
    filter(win_series) |> 
    mutate(across(win_round, as.integer)) |> 
    group_by(series_id) |> 
    summarize(
      wins = max(cumu_w),
      losses = max(cumu_l),
      ws = paste0(win_round, collapse = '-')
    ) |> 
    ungroup() |> 
    mutate(n_rounds = wins + losses) |> 
    unite(
      record, wins, losses, sep = '-'
    ) |>
    count(record, n_rounds, ws, sort = TRUE) |> 
    mutate(prop = n / sum(n))
}

summarize_cod_round_arrangements <- partial(
  summarize_round_arrangements,
  .max_round = 11,
  .adj = 0
)

@@

  actual_round_streaks <- rounds |> 
    summarize_round_arrangements(.max_round = .max_round, .adj = .adj)

@@

```{r}
load_qs('cod_round_win_prop_after_x_wins_y_rounds')
ggsci_orange <- extract_ggsci_mid_color('orange')
p_cod_round_win_prop_after_x_wins_y_rounds <- cod_round_win_prop_after_x_wins_y_rounds |> 
  filter(win_streak == 3) |> 
  mutate(
    is_signif = case_when(
      gt_is_signif ~ 'Better',
      lt_is_signif ~ 'Worse',
      TRUE ~ 'Neither'
    )
  ) |> 
  # filter(win_streak %in% c(3, 4)) |> 
  # filter(n >= 20) |> 
  ggplot() +
  geom_tile(
    color = blackish_background,
    height = 0.8,
    aes(
      fill = is_signif,
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  geom_richtext(
    fill = NA_character_,
    label.color = NA_character_,
    family = font,
    color = blackish_background,
    size = 11 / .pt,
    fontface = 'bold',
    aes(
      label = sprintf(
        '%s %s <span style="color:white">%s</span><br/>(%s)',
        scales::percent(prop, accuracy = 1), 
        case_when(
          round(prop, 1) == round(expected_poststreak_p, 1) ~ '=',
          prop >= expected_poststreak_p ~ '>=', 
          TRUE ~ '<'
        ),
        scales::percent(expected_poststreak_p, accuracy = 1),
        scales::comma(n)
      ),
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  guides(
    fill = guide_legend(
      'Significantly better/worse?'
    )
  ) +
  scale_x_continuous(
    labels = 4:11,
    breaks = seq(4.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  scale_fill_manual(
    values = c(ggsci_cyan, ggsci_grey, ggsci_orange),
    labels = c('Better', 'Neither', 'Worse')
  ) +
  theme(
    legend.position = 'top',
    legend.text = element_text(color = 'white', size = 12),
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Post win streak round win %',
    x = 'Round',
    y = '# of rounds played in series'
  ) +
  facet_wrap(~win_streak)
p_cod_round_win_prop_after_x_wins_y_rounds
save_plot_for_slide(p_cod_round_win_prop_after_x_wins_y_rounds)
```

@@

plot_round_vs_post_round_slope_chart <- function(df, .round) {
  o_win_rx_prop <- summarize_map_o_round_win_prop(df, .round)
  x1_label <- sprintf('Round %d<br/>offensive win %%', .round)
  x2_label <- sprintf('Post-round %d<br/>offensive win %%', .round)
